A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-02 02_Materials_and_Methods.Rmd
about timeseries

This data for individual graves attributed to a macroregion can be transformed to a timeseries of trait prevalence within the respective regions during the the timeframe of interest. The first step is to create a absolute occurence time series **TODO**

>>>>

This data for individual graves attributed to a macroregion can be transformed to a time series of trait prevalence within the respective regions. If a certain kind of grave can be attributed to a fuzzy point in time with radiocarbon dating, than we also know that most likely a ceremony was held around this time were the respective burial tradition was practised. That means that the cultural trait behind this behaviour must also have been present in one form or the other. An example: The idea *inhumation* must have been present in 1447 calBC in Great Britain since this year lies in the $2\sigma$ age range of the ^14^C date *NZA-32497* which was made for the Amesbury Down inhumation burial *I2639/25217*. For each year in the timeframe 2200 -- 800 calBC we can count the amount of graves with dates that cover this year with their $2\sigma$ age range. That allows the construction of regionwise time series of absolute occurrence numbers for the variables *burial type* and *burial construction* (Figure **TODO**). Although the number of dates is very small for some regions and timeperiods we still can attempt to calculate relative proportions of the mutually exclusiv traits (inhumation vs. cremation and mound grave vs. flat grave). That leads to relative timeseries of trait prevalence, which could be a powerful proxy for the development of the distribution of cultural behaviour.
